The Symmetry of Partner Modelling

### 2016-03-13 mutual-modeling.tex
Rephrase synthesis to refer to lines of thoughts from intro

In the introduction, we mentioned the controversy around the cognitive depth of
dialogues: do they build upon shallow syntactic alignment or do they entail
deeper semantic processes, which would require modelling of the partner. Our
studies rather support the second viewpoint since the quality of modelling
emerged as an intermediate variable, sensitive to some independent variables
(like the presence of awareness tools or media richness), and predictive of
dependent variables, such as task performance. We do not claim that this deeper
semantic modelling is always present in everyday conversations, but rather that
it \emph{was} indeed present in the collaborative tasks designed for our
experiments (which are representative of the tasks assigned to learners in CSCL
environments).

>>>>

In the introduction, we mentioned the controversy around the cognitive depth of
dialogues: does efficient dialogue require some modeling of what the partner
understands or intends to convey, as initially postulated by
\citet{clark1986referring}, or can dialogue simply rely on some shallow
syntactic alignment, as objected by \citet{pickering2006alignment}. While the
shallow hypothesis may be relevant to simple chat situations, we investigated
this issue in richer problem solving tasks that are more representative of the
tasks assigned to learners in CSCL environments. In four different tasks, we
found evidence that partner model each other since the quality of modelling
emerged as an intermediate variable, sensitive to several independent variables
(like the presence of awareness tools or media richness), and predictive of
several dependent variables, such as task performance or learning gains.
Thereby, even if we do not bring any definite conclusion to this debate, our
results support the CSCL school of thought in which shared understanding or
intersubjective meaning making have been a foundational concept
\citep{roschelle1995construction,schwartz1995emergence,dillenbourg2006sharing,suthers2006technology,stahl2007meaning}.
